hormones

### 2019-10-11 analysis/07_hormones.Rmd
anova functions

```{r aov}
aov1 <- aov(data = prl.char, plasma_conc ~ treatment + sex)
aov1
summary(aov1)
TukeyHSD(aov1, which = "treatment")

aov2 <- aov(data = prog.char, plasma_conc ~ treatment + sex)
aov2
summary(aov2)

aov3 <- aov(data = cort.char, plasma_conc ~ treatment + sex)
aov3
summary(aov3)
TukeyHSD(aov3, which = "treatment")

aov4 <- aov(data = est.char, plasma_conc ~ treatment )
aov4
summary(aov4)
TukeyHSD(aov4, which = "treatment")

aov5 <- aov(data = test.char, plasma_conc ~ treatment )
aov5
summary(aov5)
```

>>>>

```{r aov}

aovSexTretment <- function(mydata, whichormone){
  aov2 <- aov(data = mydata, plasma_conc ~ treatment + sex)
  print(whichormone)
  print(summary(aov2))
  print(TukeyHSD(aov2, which = "treatment"))
}
aovSexTretment(prl.char, "PRL")
aovSexTretment(cort.char, "CORT")
aovSexTretment(prog.char, "PROG")

aovTretment  <- function(mydata, whichormone){
  aov1 <- aov(data = mydata, plasma_conc ~ treatment )
  print(whichormone)
  print(summary(aov1))
  print(TukeyHSD(aov1, which = "treatment"))
}

aovTretment(est.char, "E")
aovTretment(test.char, "T")
```
